---
title: "Lab-10 Essentials of Data Analytics"
author: "Aryan Vigyat 20BCE1452"
date: "`r Sys.Date()`"
output: html_document
---
Attaching all the Libraries
```{r}
library(cluster)
library(factoextra)
```

Loading the  Dataset
```{r}
df=read.csv("USArrests.csv")
head(df,10)
summary(df)
df <- na.omit(df)
df <- scale(df[2:5])
```
1. Finding Optimal Number Clusters using Elbow Method
```{r}
set.seed(123)
fviz_nbclust(df, kmeans, method = "wss")
```
2. Apply K-Means Clustering Using k=4
```{r}
set.seed(123)
model <- kmeans(df, centers = 4)
model
```
3. Visualizing all the clusters using the Cluster Plot
```{r}
fviz_cluster(model, data = df)
```
<h4>K-Medoids</h4>
```{r}
fviz_nbclust(df, pam, method = "wss")
```
4. Applying K-medoids Algorithmn with k=4
```{r}
set.seed(123)
model1 <- pam(df, k = 4)
model1
```
5. Visualizing the clusters using cluster plot
```{r}
fviz_cluster(model1, data = df)
```
<br>
<h2>Hierarchical Clustering</h2>

```{r}
dist_matrix <- dist(df, method = 'euclidean')

set.seed(123)  
model2 <- hclust(dist_matrix, method = "average")
model2
plot(model2)
#abline(h = 2, col = "green")
```

Choosing no. of clusters, Cutting tree by number of clusters
```{r}
optimum <- cutree(model2, k = 4 )
optimum
table(optimum)
plot(model2)
rect.hclust(model2, k = 4, border = "green")
```
Time and Date Verification
```{r}
Sys.info()
Sys.time()
Sys.Date()
```
<hr>
<h2 align="center">Thank You</h2>