---
title: "LAB-5 Annova"
author: "Aryan Vigyat 20BCE1452"
date: "`r Sys.Date()`"
output: html_document
---

Attaching the libraries
```{r}
library(dplyr)
library(ggplot2)
library(boot)
```
<h3>Hypothesis</h3>
<ul>
<li>Null Hypothesis - There is no significant difference between the population means (&mu;1=&mu;2=&mu;3)</li>
<li> Alternate Hypothesis - There is siginificant difference between the means (&mu;1&ne;&mu;2&ne;&mu;3)</li>
</ul>

<h2>Question 1</h2>
1. Loading the Dataset
```{r}
df=PlantGrowth
summary(df)
head(df,5)
```
<hr>
2. Finding the Group Wise means
```{r}
df %>%
  group_by(group) %>%
  summarise(mean=mean(weight))
```
3. Boxplot
```{r}
ggplot(df, aes(x=group, y=weight)) + 
  geom_boxplot()
```
<br>
<hr>
4. Using Anova Function
```{r}
ans <-aov(weight~group,data=df)
summary.aov(ans)

```
<h3>Conclusion</h3> <br>
The value of P is less than 0.05 so we reject the Null hypothesis to conclude there is a significant difference between the population means now we check the pair wise to conclude which means differences are significant
<hr>
5. Check which pairs contribute to the difference between the means
```{r}
TukeyHSD(ans)
```
<h3>Conclusion</h3> <br>
The difference between treatment-1 and treatment-2 is significant with an adjusted p-value of 0.012 as we see can in the results obtained above.
<hr>
<h2>Question 2</h2>
1. Loading the Dataset
```{r}
df2=poisons
df2$poison=as.factor(df2$poison)
df2$treat=as.factor(df2$treat)
```
2.Group Wise Means
```{r}
df2 %>%
  group_by(poison,treat) %>%
  summarise(mean=mean(time))

```
3. Boxplot
```{r}
ggplot(df2, aes(x=poison, y=time)) + 
  geom_boxplot()+facet_wrap(df2$treat)
```
<br>
<hr>
4. Using Anova Function
```{r}
ans2 <-aov(time~poison+treat,data=df2)
summary.aov(ans2)

```
<h3>Conclusion</h3> <br>
The value of P is less than 0.05 so we reject the Null hypothesis to conclude there is a significant difference between the population means now we check the pair wise to conclude which means differences are significant
<hr>
5. Check which pairs contribute to the difference between the means
```{r}
TukeyHSD(ans2)
plot(TukeyHSD(ans2,conf.level = 0.95),las = 2)
```
<h3>Conclusion</h3> <br>
<ul>
<li> The Difference Between B-A treat and 3-1 poison is significant</li>
</ul>
Time and Date Verification
```{r}
Sys.info()
Sys.time()
Sys.Date()
```
<hr>
<h2 align="center">Thank You</h2>
<hr>