---
title: "EDA Random Forest"
author: "Aryan Vigyat 20BCE1452"
date: "2023-03-05"
output: html_document
---
```{r}
library(caTools)
library(pROC)
library(ggplot2)
library(caret)
library(e1071)
library(party)
library(knitr)
library(randomForest)
```
1. Loading the Dataset
```{r}
split <- sample.split(iris, SplitRatio = 0.7)
train <- subset(iris, split == "TRUE")
test <- subset(iris, split == "FALSE")
```
2. Building the Model using Decision Tree and Random Forest
```{r}
set.seed(120)# Setting seed
model1 = randomForest(x = train[-5], y = train$Species, ntree = 500)
summary(train)
model1
model2<- randomForest(x = train[-5], y = train$Species, ntree =100)
```
3. Predicting Using the Model
```{r}
y_pred1 = predict(model1, newdata = test[-5])
# Confusion Matrix
confusion_mtx = table(test[, 5], y_pred1)
confusion_mtx
plot(model1)
y_pred2<-predict(model2, test)
conf1<- table(test$Species, y_pred2)
conf1
plot(model2)
classer1rf<-round(mean(y_pred1!=test$Species),2)
print(paste('Accuracy For Iris for Random Forest=',1-classer1rf))
classer1dt<-round(mean(y_pred2!=test$Species),2)
print(paste('Accuracy For Iris for Decision Tree=',1-classer1dt))
```
<ul><li>The Accuracy for Iris Dataset for Random Forest is 0.93 (>80) so the model is a good fit for classification of Species</li><li>The Accuracy for Iris Dataset for Decision Tree is 0.87 (>80) so the model is a good fit for classification of Species</li></ul><hr><h2>2<sup>nd</sup> Question</h2><br>
1. Loading the Dataset
```{r}
df<- read.csv("C:/Users/ayuar/Downloads/ParisHousingClass.csv")
summary(df)
df<-na.omit(df)
head(df,10)
#Removing the not important columns
split <- sample.split(df, SplitRatio = 0.7)
train <- subset(df, split == "TRUE")
test <- subset(df, split == "FALSE")
```
2. Building the Model
```{r}
summary(train)
model1 = randomForest(x = train[-18], y = as.factor(train$category), ntree = 5)
model1
model2<- ctree(as.factor(category) ~ ., train)
```
3. Prediction using Model
```{r}
y_pred1 = predict(model1, newdata = test[-18])
# Confusion Matrix
confusion_mtx = table(test[,18], y_pred1)
confusion_mtx
plot(model1)
y_pred2<-predict(model2, test)
conf1<- table(test$category, y_pred2)
conf1
plot(model2)
classer1rf<-round(mean(y_pred1!=test$category),2)
print(paste('Accuracy For Iris for Random Forest=',1-classer1rf))
classer1dt<-round(mean(y_pred2!=test$category),2)
print(paste('Accuracy For Iris for Decision Tree=',1-classer1dt))
```
Time and Date Verification
```{r}
Sys.info()
Sys.time()
Sys.Date()
```
<hr>
<h2 align="center">Thank You</h2>
<hr>