---
title: "LAB 6 Data Visualization"
author: "Aryan Vigyat 20BCE1452"
date: "2023-02-04"
output: html_document
---
<h2>Question 1</h2>
1. Loading the Covid Dataset 
```{r}
library(readr)
library(TTR)
library(ggplot2)
states <- read.csv("C:/Users/ayuar/Downloads/states.csv")
```
2. Data Preprocessing
```{r}
states=states[complete.cases(states),]
states=states[states$State=="India",]
states=states[states$Tested!=0,]
states$Negative=states$Tested-states$Confirmed
states$Date <- as.Date(states$Date)
states$Confirmed<-c(states$Confirmed[1], diff(states$Confirmed))
states$Tested<-c(states$Tested[1], diff(states$Tested))
states$Recovered<-c(states$Recovered[1], diff(states$Recovered))
states$Negative<-c(states$Negative[1], diff(states$Negative))
states$Decreased<-c(states$Deceased[1], diff(states$Deceased))
states$Deceased<-NULL
states$Other<-c(states$Other[1], diff(states$Other))
states=states[states$Tested!=0,]
```
3. Finding Weekly and Monthly Trends
```{r}
library(dplyr)
covid_data_weekly <- states %>% 
  mutate(week = floor((as.numeric(Date) - as.numeric(min(Date))) / 7)) %>% 
  group_by(week) %>% 
  summarize(Confirmed = sum(Confirmed),
            Negative = sum(Negative),
            Recovered = sum(Recovered),
            Decreased = sum(Decreased))
covid_data_monthly <- states %>% 
  mutate(month = format(as.Date(Date), "%m"))%>% 
  group_by(month) %>% 
  summarize(Confirmed = sum(Confirmed),
            Negative = sum(Negative),
            Recovered = sum(Recovered),
            Decreased = sum(Decreased))

```
<br>
4. Identifying the Death Rate and Plotting the Weekly and Monthly Trends
```{r}
covid_data_monthly$death_rate <- covid_data_monthly$Decreased / (covid_data_monthly$Confirmed + covid_data_monthly$Negative)
covid_data_weekly$death_rate <- covid_data_weekly$Decreased / (covid_data_weekly$Confirmed + covid_data_weekly$Negative)
weeklyts<-ts(covid_data_weekly)
monthlyts<-ts(covid_data_monthly)
plot.ts(weeklyts)
plot.ts(monthlyts)
```
<br>
5. Finding the Exponential Moving Average
```{r}
timeseries_ts<-ts(states$Confirmed)
timeseries_ema <- EMA(timeseries_ts, alpha = 0.4)
plot(timeseries_ema)


```
<br>
6. ARIMA Model
```{r}
library(forecast)
arima<- auto.arima(ts(states$Confirmed))
arima_predictions <- forecast(arima, h = 12)
plot(arima_predictions)

```
<br>
<h2> Question 2</h2>

1. Loading the Dataset
```{r}
library(readr)
Apple <- read_csv("C:/Users/ayuar/Downloads/AAPL(Apple).csv")
View(Apple)
```
2. Convert into Time Series Dataset
```{r}
appletimeseries <- ts(Apple$Open, start = c(2013, 1), frequency = 405)
plot.ts(appletimeseries)
```
3. Log of timeSeries Plot
```{r}
logappletimeseries <- log(appletimeseries)
plot.ts(logappletimeseries)
```
4. Simple Moving Average
```{r}
library("TTR")
appleSMA3 <- SMA(appletimeseries,n=3)
plot.ts(appleSMA3,ylab="High")
```
5. Weighted Moving Average
```{r}
appleWMA3<-WMA(appletimeseries,n=4,wts=c(1,4,3,1), na.rm = TRUE)
library(ggplot2)
valid_indices <- (4-1)/2:(length(appletimeseries) - (4-1)/2)
library(zoo)

# Plot the original time series data and the weighted moving average
df_appletimeseries <- data.frame(time = time(appletimeseries), value = coredata(appletimeseries))
ggplot(data = df_appletimeseries, mapping = aes(x = time, y = value)) +
  geom_line(color = "red") +
  geom_line(data = df_appletimeseries[valid_indices, ], 
            mapping = aes(x = time, y = appleWMA3[valid_indices]), 
            color = "blue") +
  ggtitle("Weighted Moving Average") +
  xlab("Time") +
  ylab("Value")
```
<br>
6. Arima Model
```{r}
library(forecast)
library(forecast)

# Fit the ARIMA model
fit <- auto.arima(appletimeseries)

# Plot the residuals of the ARIMA model
plot(residuals(fit), main = "ARIMA Model Residuals", xlab = "Index", ylab = "Residual")

# Plot the ACF and PACF of the residuals
Acf(residuals(fit), main = "ACF of ARIMA Model Residuals")
Pacf(residuals(fit), main = "PACF of ARIMA Model Residuals")

# Plot the ARIMA model forecast
plot(forecast(fit), main = "ARIMA Model Forecast", xlab = "Index", ylab = "Value")
arima_predictions <- forecast(fit, h = 12)
plot(arima_predictions)

```

7. Seasonal Arima
```{r}
arima_model <- auto.arima(appletimeseries, seasonal = TRUE)

# Make predictions using the ARIMA model
arima_predictions <- forecast(arima_model, h = 12)

# Plot the original time series data and the ARIMA predictions
plot(arima_predictions)
```

