---
title: "LAB 3 Data Visualization"
author: "Aryan Vigyat 20BCE1452"
date: "2023-01-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Instantiating the Required Libraries<br>
```{r}
library(dplyr)
library(readr)
library(corrplot)
library(RColorBrewer)
library(ggplot2)
library(GGally)
```

1. Loading the Dataset
```{r}
df=read_csv("C:/Users/ayuar/Downloads/churn_data.csv.zip")
head(df,5)
df<-na.omit(df)
```
<br>
2. Selecting the Attributes for Correlation
```{r}
df <- df %>%
  select_if(is.numeric)
M<-cor(df[,4:12])
```
<br>
3. Drawing all the Correlation Plots
```{r}
corrplot(M,method="pie",order="hclust",
         col=brewer.pal(n=8, name="RdYlBu"))
corrplot(M, method = "square",order="hclust",
         col=brewer.pal(n=8, name="RdYlBu"))
corrplot(M, method = "circle",order="hclust",
         col=brewer.pal(n=8, name="RdYlBu"))
corrplot(M, type="upper",order="hclust",
         col=brewer.pal(n=8, name="RdYlBu"))
corrplot.mixed(M)

```
<br>
4. Scatterplots for checking correlation
```{r}
ggplot(df,aes(x=age,y=deposits))+geom_point()+ggtitle("Age vs Deposits")+xlab("Age")+ylab("Deposits")
ggpairs(df[,1:5])

```
<br>
2<sup>nd</sup> Dataset - (Orange)

```{r}
library(datasets)
summary(Orange)
View(Orange)
head(Orange,5)
```
Question 1: Age is a Ratio Variable,Circumference is a ratio Variable and Tree is a Interval Data Type
<br>
Question 2:
```{r}
mean(Orange$circumference)
sd(Orange$circumference)
sd(Orange$circumference)/sqrt(length((Orange$circumference)))
```
Question 3:
<br>
```{r}
model1<-lm(circumference~age,data=Orange)
model1
```
Coefficients 
<ul>
  <li>Intercept means the constant in the Y Axis.</li>
  <li>The Second Value Give the Slope of the Linear Model</li>
</ul>
Question 4:
<br>
```{r}
model2<-lm(age~circumference,data=Orange)
summary(model1)
summary(model2)
```
Question 5:
Inferences
<ul>
  <li>The R-Square Value for the both the models is 0.83 so 83 percent of the variance in the Dataset is explained by the Model and also Considering the P-Value (<0.05) so we Say the Model is a good fit</li>
  <li>For the First Model the median is closer to 0 than the Second model</li>
</ul>
<br>
Question 6:
<br>
```{r}
x=Orange$age
y=Orange$circumference
pcor=cor(x,y,method="pearson")
print(pcor)
```
Its closer to 1, so strongly correlated
<br>
Question 7:<br>
Yes The P-Value obtained is 1.931e-14. value of less than 0.05 .Therefore you determine,that it is statistically significant.

