---
title: "Lab 7 Data Visualization SNA"
author: "Aryan Vigyat 20BCE1452"
date: "2023-02-13"
output: html_document
---

Attaching the Libraries
```{r}
library(sna)
library(igraph)
```

1. Import and load the dataset and view information about it using str() function.

```{r}
df <-read.csv("~/socialnetworkdata.csv")
data <- data.frame(df$first,df$second)
str(data)
```
2. Create the graph network using graph.data.frame() function.
```{r}
graph <- graph.data.frame(data)
V(graph)
E(graph)
igraph::degree(graph)  
igraph::betweenness(graph)
V(graph)$label <- V(graph)$name 
V(graph)$degree <- igraph::degree(graph)
```
3. Plot the Histogram graph For Node Degrees.
```{r}
hist(V(graph)$degree,main='Histogram of node degree',xlab='Degree of vertices',ylab='Frequency')
```
4. Plot the Network Graph Diagram.
```{r}
plot(graph,vertex.label.cex=0.7,vertext.size=2,edge.arrow.size=0.1)
```
<br>
5. Compute the hub and authority scores and depict the vertices with maximum hub and authority in the network diagram.
```{r}
hs <- hub_score(graph)$vector
hs
as <- authority.score(graph)$vector
as
```

```{r}
plot(graph,vertex.size=hs*30,main='Hubs',edge.arrow.size=0.1,layout=layout.fruchterman.reingold)
```

```{r}

plot(graph,vertex.size=as*30,main='Authorities',edge.arrow.size=0.1,layout=layout.fruchterman.reingold)
```
<br>
6. Find out the communities present in the network.
```{r}
network <- graph.data.frame(data,directed=F)
cnetwork <- cluster_edge_betweenness(network)
plot(cnetwork,network,vertex.label.cex=0.7)
```
```{r}
# (vii) Conclusion

#In social network research, the SNA and igraph packages in R were utilized to analyze a dataset with network data involving different nodes. By computing the hub and authority scores of each node, a network diagram was created. The identification of communities in the network revealed that nodes within the same group were highly connected, while nodes between different groups were only weakly connected.
```

